Abstract Binding Trees

### 2015-10-21 paper.tex
Fix one I missed

Let $\Symbols$ be an infinite set of symbols; let $\Finsets$ be the free
cocartesian category over $\Symbols\times\Sorts$. Then, fix a covariant presheaf of operators
$\Operators:\Finsets\times\Arities\to\Sets$ such that the arrows in $\Finsets$
lift to renamings of operators' parameters; via the Grothendieck construction,
we can also consider the set $\int\Operators$ of operators
$(U,\varrho,\vartheta)$ for $\Member{\vartheta}{\Operators(\Upsilon,\varrho)}$.

>>>>

Let $\Symbols$ be an infinite set of symbols; let $\Finsets$ be the free
cocartesian category over $\Symbols\times\Sorts$. Then, fix a covariant
presheaf of operators $\Operators:\Finsets\times\Arities\to\Sets$ such that the
arrows in $\Finsets$ lift to renamings of operators' parameters; via the
Grothendieck construction, we can also consider the set $\int\Operators$ of
operators $(\Upsilon,\varrho,\vartheta)$ for
$\Member{\vartheta}{\Operators(\Upsilon,\varrho)}$.
